---
output: github_document
---

## Purpose of this repo 

The goal of this repo is to provide a list of the JavaScript libraries that have been adapted in R, so that R developers don't lose too much time trying to determine if a particular JavaScript library has already been ported in R. 

## How to contribute

This repo is meant to be a collaborative effort (I can't list all adaptations by myself). The packages that are displayed in the [htmlwidgets gallery](https://gallery.htmlwidgets.org/) are automatically added to this list every Sunday just before midnight UTC. 

**To contribute, you only need to add an R package and the Javascript libraries it uses in `other_packages.csv`.** No need to render the R Markdown file, this will be done automatically via GitHub actions once your PR is accepted (it will take a few minutes to update the README).

## List

```{r echo = FALSE}
source("list_htmlwidgets.R")
```

```{r echo = FALSE}
library(knitr)

kable(output, col.names = c("R Packages", "JavaScript libraries"))
```

